Central Limit Theorems for Super Ornstein-Uhlenbeck Processes with stable Branching

### 2019-09-11 supCLT.tex
change supCLT.tex

\subsection{An outline of the methodology}
Let us give some intuitive explanation of the methodology used in this paper.
For any $\mu\in \mathcal M_c(\mathbb R^d)$ and any random variable $Y$ with finite mean, we define
$
  \mathcal I_s^t Y
  := \mathcal I_s^t [Y, \mu]
  := \mathbb P_\mu[Y|\mathscr F_t] - \mathbb P_\mu[Y|\mathscr F_s]
$
  where $0 \leq s \leq t <\infty.$
We will use the shorter notation $\mathcal I_s^t Y$ when there is no danger of confusion.
For $f\in \mathcal{P}$, consider the following decomposition over the time interval $[0,t]$:
\begin{align}
  X_t(f)
  := \sum_{k=0}^{\lfloor t \rfloor-1} \mathcal I_{t-k-1}^{t-k} X_t (f)+\mathcal I_0^{t-\lfloor t \rfloor} X_t(f) + X_0( P^\alpha_tf),
  \quad t\geq 0.
\end{align}
To find the fluctuation of $X_t(f)$, we will investigate the fluctuation of each term on the right hand side above.
The second term and third term are negligible after the rescaling, and for the first term we will establish
a multi-variate unit interval CLT  which says that
\[
  \Big( \|X_t\|^{-\frac{1}{1+\beta}}\mathcal I^{t-k}_{t-k-1} X_t(f) \Big)_{k=0}^n
  \xrightarrow [t\to \infty]{d} (\zeta^f_k)_{k=0}^n,
\]
where $(\zeta^f_k)_{k \in \mathbb N}$ are independent $(1+\beta)$-stable random variables.
If $f \in \mathcal C_s\setminus\{0\}$, then it can be argued that $\sum_{k=0}^{\lfloor t \rfloor} \xi^f_k \xrightarrow[t\to \infty]{d} \zeta^f$ and then intuitively we have
\(
  \|X_t\|^{-\frac{1}{1+\beta}}  X_t(f)
  \xrightarrow[t\to \infty]{d} \zeta^f.
  \)
If $f \in \mathcal C_c \setminus \{0\}$, then it can be argued that
\(
t^{-\frac{1}{1+\beta}} \sum_{k=0}^{\lfloor t\rfloor} \zeta_k \xrightarrow[t\to \infty]{ d} \zeta^f
\)
and then intuitively we have
\(
\|tX_t\|^{-\frac{1}{1+\beta}}  X_t(f)
\xrightarrow[t\to \infty]{d} \zeta^f.
\)
If $f\in \mathcal C_l$, the general idea is almost the same, except that we need to consider the decomposition over the time interval $[t,\infty)$.

>>>>

\subsection{An outline of the methodology}
Let us give some intuitive explanation of the methodology used in this paper.
For any $\mu\in \mathcal M_c(\mathbb R^d)$ and any random variable $Y$ with finite mean, we define
$
  \mathcal I_s^t Y
  := \mathcal I_s^t [Y, \mu]
  := \mathbb P_\mu[Y|\mathscr F_t] - \mathbb P_\mu[Y|\mathscr F_s]
$
  where $0 \leq s \leq t <\infty.$
We will use the shorter notation $\mathcal I_s^t Y$ when there is no danger of confusion.
For $f\in \mathcal{P}$, consider the following decomposition over the time interval $[0,t]$:
\begin{align}
  X_t(f)
  := \sum_{k=0}^{\lfloor t \rfloor-1} \mathcal I_{t-k-1}^{t-k} X_t (f)+\mathcal I_0^{t-\lfloor t \rfloor} X_t(f) + X_0( P^\alpha_tf),
  \quad t\geq 0.
\end{align}
To find the fluctuation of $X_t(f)$, we will investigate the fluctuation of each term on the right hand side above.
The second term and third term are negligible after the rescaling, and for the first term we will establish
a multi-variate unit interval CLT  which says that
\[
  \Big( \|X_t\|^{-\frac{1}{1+\beta}}\mathcal I^{t-k}_{t-k-1} X_t(f) \Big)_{k=0}^n
  \xrightarrow [t\to \infty]{d} (\zeta^f_k)_{k=0}^n,
\]
where $(\zeta^f_k)_{k \in \mathbb N}$ are independent $(1+\beta)$-stable random variables.
If $f \in \mathcal C_s\setminus\{0\}$, then it can be argued that $\sum_{k=0}^{\lfloor t \rfloor} \zeta^f_k \xrightarrow[t\to \infty]{d} \zeta^f$ and then intuitively we have
\(
  \|X_t\|^{-\frac{1}{1+\beta}}  X_t(f)
  \xrightarrow[t\to \infty]{d} \zeta^f.
  \)
If $f \in \mathcal C_c \setminus \{0\}$, then it can be argued that
\(
t^{-\frac{1}{1+\beta}} \sum_{k=0}^{\lfloor t\rfloor} \zeta_k \xrightarrow[t\to \infty]{ d} \zeta^f
\)
and then intuitively we have
\(
\|tX_t\|^{-\frac{1}{1+\beta}}  X_t(f)
\xrightarrow[t\to \infty]{d} \zeta^f.
\)
If $f\in \mathcal C_l$, the general idea is almost the same, except that we need to consider the decomposition over the time interval $[t,\infty)$.
